---
title: "cm010"
author: "sdhanani"
date: "October 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```

```{r}
left_join()
inner_join()
full_join()
anti_join()
semi_join()
??join ##for other joins but at the moment this is enough ##
```

```{r}
install.packages("devtools")
library(devtools)
install_github("JoeyBernhardt/singer")
```

Now we have the singer dataframes

```{r}
library(singer)
```

and then we load into the environment the datasets

```{r}
data("locations")
data("songs")
```

and we can give a look at them

```{r}
glimpse(songs)
```
```{r}
glimpse(locations)
```

```{r}
View(songs)
View(locations)
```

### Dataframe with Release and Year

Produce a dataframe with all the albums, the artists and the year in which the album was published. 

```{r}
left_join(locations, songs)

## version done in class below ##
relartyear<- inner_join(locations, songs, by=c("title", "artist_name")) %>% 
  select(release, artist_name, year)

View(relartyear)
## not anit-join, full_join: adds rows from one table to the other, keeps all the information but in our case produces too many columns, semi_join: doesn't merge columns from one dataframe to another. left_join: still has an NA in it

View(inner_join(locations, songs, by="title"))
```

### challenge 1

Get the number of releases per year.

```{r}
songs %>% 
  arrange(year)

## now done in class ##

inner_join(songs, locations, by="title") %>% 
  count(year)
```


## RESHAPING  

```{r}
data("singer_locations")
glimpse(singer_locations)
?singer_locations

View(singer_locations)
```

Want: year, artist_hotttnesss, artist_familiarity, duration

```{r}
hfd_y <- singer_locations %>% 
  select(year, artist_hotttnesss, artist_familiarity, duration)

hfd_y %>% 
  filter(year >1900) %>% 
  ggplot(aes(x= year, y=artist_hotttnesss)) +
  geom_point()
```

package `tidyr`, `gather()`: from wide to long format

```{r}

hfd_y_long<-hfd_y %>% 
  gather(key="Measure", value="Units", artist_hotttnesss:duration)

View(hfd_y_long)
View(hfd_y)

hfd_y_long %>%
  filter(year>1900) %>% 
  ggplot(aes(x=year, y=Units)) +
  geom_point() +
  facet_wrap(~Measure) +
  scale_y_log10()
```


**WIDE** dataframe
**LONG** dataframe
